A Study of Residual Adapters for Neural Machine Translation

### 2020-08-14 2020/wmt_20/emnlp2020.tex
changed title

\newcommand{\mpTodo}[1]{\Todo[MP:]{\textcolor{green}{#1}}}
\newcommand{\mpDone}[1]{\done[MP]\Todo[MP:]{\textcolor{green}{#1}}}
\usepackage{mathtools,xparse}
\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
\NewDocumentCommand{\normL}{ s O{} m }{%
  \IfBooleanTF{#1}{\norm*{#3}}{\norm[#2]{#3}}_{L_2}%
}
\newcommand{\src}{\ensuremath{\mathbf{f}}} % source sentence
\newcommand{\trg}{\ensuremath{\mathbf{e}}} % target sentence
\newcommand{\domain}[1]{\texttt{\textsc{#1}}}
\newcommand{\system}[1]{\texttt{\textbf{#1}}}
\newcommand{\vlambda}{\ensuremath{\boldsymbol\lambda}\xspace} % parameters vector for a distribution
\newcommand{\indic}[1]{\ensuremath{\mathbb{I}(#1)}}
% \newcommand{\SB}[1]{\textcolor{green}{#1}}
% \newcommand{\SW}[1]{\textcolor{red}{#1}}
\newcommand{\SB}[1]{\textbf{#1}}
\newcommand{\SW}[1]{\underline{#1}}
\renewcommand\textfraction{.1}
\renewcommand\floatpagefraction{.95}

@@

\title{Ablation study on the residual adapter in Neural Machine Translation}

@@

Weight decay applies a penalization on weights of the adapters.
\begin{equation}
  \begin{split}
    \bar{L} & = \mathop{\sum}_{x,y} (log(P(y|x)) \\
    & + \lambda * \sum_{i \in \{1,..,6\} \otimes \{enc, dec\}} \normL{\theta_{\operatorname{ADAP}^{(i)}}})
  \end{split}
\end{equation}

>>>>

\newcommand{\mpTodo}[1]{\Todo[MP:]{\textcolor{green}{#1}}}
\newcommand{\mpDone}[1]{\done[MP]\Todo[MP:]{\textcolor{green}{#1}}}
\usepackage{mathtools,xparse}
\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
\NewDocumentCommand{\normL}{ s O{} m }{%
  \IfBooleanTF{#1}{\norm*{#3}}{\norm[#2]{#3}}_{2}%
}
\newcommand{\src}{\ensuremath{\mathbf{f}}} % source sentence
\newcommand{\trg}{\ensuremath{\mathbf{e}}} % target sentence
\newcommand{\domain}[1]{\texttt{\textsc{#1}}}
\newcommand{\system}[1]{\texttt{\textbf{#1}}}
\newcommand{\vlambda}{\ensuremath{\boldsymbol\lambda}\xspace} % parameters vector for a distribution
\newcommand{\indic}[1]{\ensuremath{\mathbb{I}(#1)}}
% \newcommand{\SB}[1]{\textcolor{green}{#1}}
% \newcommand{\SW}[1]{\textcolor{red}{#1}}
\newcommand{\SB}[1]{\textbf{#1}}
\newcommand{\SW}[1]{\underline{#1}}
\renewcommand\textfraction{.1}
\renewcommand\floatpagefraction{.95}

@@

% -- \title{Ablation study on the residual adapter in Neural Machine Translation}
\title{A Study of Residual Adapters for Neural Machine Translation}

@@

Weight decay applies a penalization on the weights of the adapters.\fyTodo{The second summation also runs over $x,y$ ? I think not}
\begin{equation}
  \begin{split}
    \bar{L} & = \mathop{\sum}_{x,y} (log(P(y|x)) \\
    & + \lambda * \sum_{i \in \{1,..,6\} \otimes \{enc, dec\}} \normL{\theta_{\operatorname{ADAP}^{(i)}}})
  \end{split}
\end{equation}
